\documentclass[sigconf, review=true]{acmart}
%Do not remove the review=true option for papers submitted for review to ICVGIP2021.

\usepackage{booktabs} % For formal tables

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI  - Required only for Camera Ready
%\acmDOI{10.475/123_4}

% ISBN - Required only for Camera Ready
%\acmISBN{123-4567-24-567/08/06}

%Conference

\acmConference[ICVGIP'21]{12th Indian Conference on Computer Vision, Graphics and Image Processing}{December 2021}{Jodhpur, India}
\acmYear{2021}
\copyrightyear{2021}

\acmPrice{15.00}

\begin{document}
\title{Simultaneous Segmentation of Blood Vessels and Optic Disc in Fundal Images using Multi-tasking Deep Neural Network}
\titlenote{Produces the permission block, and
  copyright information}

\author{Submission Id 108}
\affiliation{%
  \institution{}
  \streetaddress{}
  \city{}
  \state{}
  \country{}
  \postcode{}
}


% The default list of authors is too long for headers.
\renewcommand{\shortauthors}{}


\begin{abstract}
Fundal imaging is the most commonly used non-invasive technique for early detection of many retinal diseases like diabetic retinopathy.
An initial step in automatic processing of fundal images for detecting diseases is to identify the various landmark regions in the retinal image.
The most important regions visible in fundal image are the optic disc, blood vessels and fovea.
In this work, we propose a multi-tasking deep learning architecture for segmenting both optic disc and blood vessels simultaneously.
Our experimental results show that combined predictions of optic disc and blood vessels  perform significantly better compared to individual predictions.
We achieved an F1 score of 0.78 for blood vessels segmentation, on the DRIVE test dataset, with multi-tasking using a simple U-Net architecture.
When the same architecture is used without multi-tasking, i.e. for blood vessel segmentation alone, the F1 score was 0.72 which is significantly less compared to the multi-tasking model performance.
Similarly for optic disc segmentation, we obtained an F1 score of 0.76 using multi-tasking which is a significant improvement over 0.7 without multi-tasking.
We also performed experiments on HRF dataset.
We got an F1 score of 0.79 with multi-tasking and 0.78 without multi-tasking on HRF dataset for blood vessel segmentation.
Using a more complex architecture, like Laddernet, it is possible to further improve the results.

\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10010147.10010257.10010258.10010262</concept_id>
<concept_desc>Computing methodologies~Multi-task learning</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computing methodologies~Multi-task learning}
\keywords{Fundal Image, Blood Vessel Segmentation, Multi-tasking, Deep Neural Networks}


\maketitle

\input{samplebody-conf}

\bibliographystyle{ACM-Reference-Format}
\bibliography{ICVGIP-Latex-Template}

\appendix


\end{document}
